Democracy, Public Support, and Measurement Uncertainty

### 2021-05-13 paper/dcpo_demsupport.Rmd
theta with errors

>>>>

\pagebreak
```{r datawitherrors}

ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

df_cls_errors <- purrr::map(1:900, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta")  %>%
    mutate(iter = anEntry) 
  }
  )

cls_theta_uncertainty <- bind_rows(df_cls_errors)
saveRDS(cls_theta_uncertainty,"data/cls_theta_uncertainty.rds")

ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpo <- purrr::map_df(1:900, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta") %>%
    mutate(iter = anEntry) %>%
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country"))
})

saveRDS(df_dcpo,"dcpo_theta_uncertainty.rds")
